% LaTeX Curriculum Vitae Template
%
% Copyright (C) 2004-2009 Jason Blevins <jrblevin@sdf.lonestar.org>
% http://jblevins.org/projects/cv-template/
%
% You may use use this document as a template to create your own CV
% and you may redistribute the source code freely. No attribution is
% required in any resulting documents. I do ask that you please leave
% this notice and the above URL in the source code if you choose to
% redistribute this file.

\documentclass[letterpaper]{article}

\usepackage{hyperref}
\usepackage{geometry}

% Comment the following lines to use the default Computer Modern font
% instead of the Palatino font provided by the mathpazo package.
% Remove the 'osf' bit if you don't like the old style figures.
\usepackage[T1]{fontenc}
\usepackage[sc,osf]{mathpazo}

% Set your name here
\def\name{Angdi Lu}

% Replace this with a link to your CV if you like, or set it empty
% (as in \def\footerlink{}) to remove the link in the footer:
\def\footerlink{http://jblevins.org/projects/cv-template/}

% The following metadata will show up in the PDF properties
\hypersetup{
	colorlinks = true,
	urlcolor = black,
	pdfauthor = {\name},
	pdfkeywords = {economics, statistics, mathematics},
	pdftitle = {\name: Curriculum Vitae},
	pdfsubject = {Curriculum Vitae},
	pdfpagemode = UseNone
}

\geometry{
	body={6.5in, 8.5in},
	left=1.0in,
	top=1.25in
}

% Customize page headers
\pagestyle{myheadings}
\markright{\name}
\thispagestyle{empty}

% Custom section fonts
\usepackage{sectsty}
\sectionfont{\rmfamily\mdseries\Large}
\subsectionfont{\rmfamily\mdseries\itshape\large}

% Other possible font commands include:
% \ttfamily for teletype,
% \sffamily for sans serif,
% \bfseries for bold,
% \scshape for small caps,
% \normalsize, \large, \Large, \LARGE sizes.

% Don't indent paragraphs.
\setlength\parindent{0em}

% Make lists without bullets
\renewenvironment{itemize}{
	\begin{list}{}{
			\setlength{\leftmargin}{1.5em}
		}
	}{
	\end{list}
}

\begin{document}
	
	% Place name at left
	{\huge \textbf{\name}}
	
	% Alternatively, print name centered and bold:
	%\centerline{\huge \bf \name}
	
	\vspace{0.25in}
	
	\begin{minipage}{0.5\linewidth}
		\href{http://www.ruc.edu.cn/}{Renmin University of China} \\
		School of Applied Economics \\
 Office	 407C, Mingde Main building \\
	 Zhongguancun Street 59, Beijing, China
	\end{minipage}
	\begin{minipage}{0.45\linewidth}
		\begin{tabular}{ll}
			Phone: & (86) 15650704120 \\
			Email: & \href{mailto:angdilu@ruc.edu.cn}{\tt angdilu@ruc.edu.cn} \\
			Homepage: & \href{http://angdi-lu.com/}{\tt http://angdi-lu.com/} \\
		\end{tabular}
	\end{minipage}
	
	\section*{\textbf{Employment}}
	
	\begin{itemize}
  \item Associate Professor, Renmin University, 2023.9-present.  
		\item Assistant Professor, Renmin University, 2020.8-2023.8.  
	\end{itemize}

\section*{\textbf{Education}}
	\begin{itemize}
	\item Ph.D. in Economics, Singapore Management University, 2020.
	\item B.A. in Economics, Fudan University, 2015.
	\end{itemize}

\section*{\textbf{Research fields}}
\begin{itemize}
	\item Primary fields: International Trade, Economic Geography
	\item Secondary fields: Development Economics, Environmental Economics  
\end{itemize}

	\section*{\textbf{Research}}
	\subsection*{Publications}
	
	\begin{itemize}
		\item[1.]   Imports of Key Capital Goods and Quality Upgrading: Evidence from China’s Import Subsidy Policy (with Jie Li and Shuang Wu), {\it  China Economic Review}, 2023. 
			\item[2.]  The Impact of Export VAT Rebate Reduction on Firms' Pollution Emissions: Evidence from Chinese Enterprises  (with Jiang Zhang and Jie Li), {\it  Energy Economics}, 2023.
			\item[3.] The  Pro‐competitive Effects of Indirect Export Exposures: Evidence from China  (with Jie Li),  \textit{the World Economy}, accepted.
	\end{itemize}
	
	\subsection*{Working papers}
	
	\begin{itemize} 
		\item[1.] Growing Beyond Trade: Export Shocks and the Spatial Expansions of Bank Branching  (\textit{R\&R}  at  \textit{the World Economy}).
	\item[2.]  Beyond Wealth: The Impact of Robot Adoption on Chronic Diseases (\textit{R\&R}  at  \textit{the Health Economics}).	
	\item[3.] Quantifying Quality Specialization Across Space: Skills, Sorting, and Agglomeration.
	\item[4.]  Cultural Differences and Collaborative Innovation Across Space.
	\item[5.]  Environmental Regulation, Local Production Networks and Pollution Outsourcing. 
	\end{itemize}

\section*{\textbf{Grants}}
	\begin{itemize} 
 \item[1.] Single PI, PKU-Lincoln Institute Center awards research fellowships, 2023-2024. (80, 000 RMB)
\item[2.] Single PI, Young Scholar Funding, National Natural Science Foundation of China, 2024-2026. (300, 000 RMB)
	\item[3.] Single PI, New Faculty Start-up Funding, 2021-2023. (50, 000 RMB)
	\end{itemize}

\section*{\textbf{Seminar and conferences}}
2024: NUS LKYSPP ACI annual conference; YNU trade and urban economics workshop 
2023: $\mathrm{NUST}^*$ Seminar, NJU workshop, $\mathrm{SPKU}^*$, AMES (THU), $\mathrm{SYSU}^*$, RUC Seminar; 2022: RUC Seminar; 2021: China Economics Annual Meeting; 2019: FDU Seminar, ShanghaiTech Seminar, WHU Seminar, HUST Seminar, ZUEL Seminar, CUEB Seminar,  Asia-Pacific Trade Seminar, Biennial Conference of China Development Studies (SJTU), Industrial Organization and Growth Conference (Nanjing Audit), Singapore Economic Review Conference,  SMU Conference on Urban and Regional Economics\\
($*$ presented by coauthors)
		
 \section*{\textbf{Teaching}}
 Renmin University: Advanced Mathematical Economics (Ph.D and master., 2020/2021/ 2022/2023),  Spatial Economics (Ph.D., 2022/2023), International Economics (Undergraduate, 2020/2021/2022/2023).   \\
Singapore Management University: International Economics B (Undergraduate, 2019).
 
 \section*{\textbf{Referee services}}
\textit{Emerging Markets Finance and Trade, Economic Inquiry, Economics of Transition and Institutional Change, Taiwan Economic Review, Review of International Economics.}


 \section*{\textbf{Others}}
 Born: 1992/5\\
 Gender: Female\\
 Computer Skills: Matlab, Julia, Stata, ArcGIS, API (R and Python)\\
 Languages: English (fluent), Mandarin (native), Cantonese (native)
		
	\bigskip
	
	% Footer
	\begin{center}
		\begin{footnotesize}
			Last updated: \today 
		\end{footnotesize}
	\end{center}
	
\end{document}
